An Example Article

### 2023-05-26 article-en/article-temp-header.tex
update

% package for section etc.
\usepackage{titlesec}
\titleformat{\section}{\large\bfseries}{\thesection.}{1.2ex}{}
\titleformat{\subsection}{\normalfont\bfseries}{\thesubsection.}{1.2ex}{}
\titleformat{\subsubsection}{\normalfont\slshape}{\thesubsubsection.}{1.2ex}{}

@@

% headers and footers setting
%\pagestyle{fancy}
%\fancyhf{}
%\fancyhead[CO]{\uppercase{Title of Paper}}
%\fancyhead[CE]{\uppercase{Author A, Author B \& Author C}}
%\fancyfoot[C]{\thepage}
%\renewcommand{\headrulewidth}{0pt}

%\fancyhead[C]{\uppercase{Title of Paper}}
%\fancyfoot[C]{\thepage}
%\renewcommand{\headrulewidth}{0pt}

\makeatletter
\pagestyle{fancy}
\fancyhf{}
\fancyhead[CO]{\@shorttitle}
\fancyhead[CE]{\@shortauthor}
\fancyhead[RO]{\thepage}
\fancyhead[LE]{\thepage}
\makeatother

@@

\shorttitle{Short Title of Article}
\shortauthor{Author A, Author B, and Author C}

\author[1]{Author A\thanks{Email address: \texttt{A.A@university.edu}; Corresponding author.}}
\author[1]{Author B\thanks{Email address: \texttt{B.B@university.edu}}}
\author[2]{Author C\thanks{Email address: \texttt{C.C@university.edu}}}
%\author[2]{Author D\thanks{Email address: \texttt{D.D@university.edu}}}
\affil[1]{Department of Mathematics, \LaTeX\ University}
\affil[2]{Department of Mechanical Engineering, \LaTeX\ University}

@@

\bibliographystyle{plain}
%\bibliographystyle{abbrv}

\bibliography{reference}

>>>>

% package for section etc.
\usepackage{titlesec}
\titleformat{\section}{\large\bfseries}{\thesection.}{1.2ex}{}
\titleformat{\subsection}{\normalfont\bfseries}{\thesubsection.}{1.2ex}{}
\titleformat{\subsubsection}{\normalfont\itshape}{\normalfont\thesubsubsection.}{1.2ex}{}

% hyperlink setting
\hypersetup{
  colorlinks = true,
  linkcolor = magenta,
  citecolor = blue,
  filecolor = blue,
  urlcolor = blue,
}

@@

% headers and footers setting
%\pagestyle{fancy}
%\fancyhf{}
%\fancyhead[CO]{\footnotesize\uppercase{Title of Paper}}
%\fancyhead[CE]{\footnotesize\uppercase{Author A, Author B \& Author C}}
%\fancyfoot[C]{\footnotesize\thepage}
%\renewcommand{\headrulewidth}{0pt}

%\fancyhead[C]{\footnotesize\uppercase{Title of Paper}}
%\fancyfoot[C]{\footnotesize\thepage}
%\renewcommand{\headrulewidth}{0pt}

\makeatletter
\pagestyle{fancy}
\fancyhf{}
\fancyhead[CO]{\footnotesize\MakeUppercase{\@shorttitle}}
\fancyhead[CE]{\footnotesize\MakeUppercase{\@shortauthor}}
\fancyhead[RO]{\footnotesize\thepage}
\fancyhead[LE]{\footnotesize\thepage}
\renewcommand{\headrulewidth}{0pt}
\makeatother

@@

% Short title for running heads:
\shorttitle{A posteriori error analysis for CG methods for PDDEs}

\author[1]{Author A}
\author[2]{Author B}
\author[1]{Author C\thanks{Email address: \texttt{xyz@math.univ.edu}; Corresponding author.}}
\affil[1]{Department of Mathematics, \LaTeX\ University}
\affil[2]{Department of Mechanical Engineering, \LaTeX\ University}

% Short list of authors for running heads:
\shortauthor{Author A, Author B, and Author C}

@@

% References
\bibliographystyle{plain}
%\bibliographystyle{abbrv}

\phantomsection
\addcontentsline{toc}{section}{\refname}
\bibliography{reference}
